Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2024-04-19 revision-1/lang.tex
checkpoint

>>>>

Eliminating cheating by adding information theoretically secure MAC
codes to shares is a fundamental approach accomplished by protocols
including BDOZ \cite{XXX} and SPDZ \cite{XXX}.  These protocols assume
pre-processing that distributes shares with MAC codes to all clients.
This integrates well with pre-processed Beaver Triples to implement
malicious secure and relatively efficient multiplication \cite{XXX}.
Here we show how to implement malicious secure two party multiplication
in the BDOZ style via some extensions of $\minifed$.
